Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2020-04-06 vesicle_code/docs/permeableVes/main.tex
uncommenting tikz figures
working on relaxation section

We consider a single semi-permeable vesicle in a quiescent flow. For
impermeable vesicles, the vesicle relaxes to a shape where the tension
$\Lambda$ is constant and negative~\cite{kra-win-sei-lip1996}. In the
semi-permeable case, the area of the vesicle is governed by
equation~\eqref{eqn:areaROC}, where $\beta > 0$. We expect the
semi-permeable vesicle to reach a steady-state shape, meaning that in
the limit,
\begin{align}
  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
  \rightarrow 0.
\end{align}
Based on numerical observations, the steady-state shape is a circular
vesicle with constant tension. Since the tension and curvature are
constant, we can solve for the curvature in terms of the tension $\kappa
= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
\begin{align}
  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
\end{align}
which is constant by the local inextensibility constraint. Therefore, we
can compute the final tension in terms of the length using the formula
\begin{align}
  \Lambda = \frac{2\pi^2}{L^2}.
  \label{eqn:finalTension}
\end{align}
Therefore, in contrast to a impermeable vesicle, the final tension is
positive rather than negative.

We start by simulating a star-shaped vesicle in a quiescent flow with
semi-permeability rate $\beta=1$. The vesicle shape at five time
steps is in Figure~\ref{fig:starShape}. To perform this simulation,
we use an adaptive second-order time stepping
method~\cite{qua-bir2016}. The times and reduced areas are
in the titles, and note that the shapes are not eqiuspaced in time.

\begin{figure}[htp]
  \begin{center}
    \input{figures/starRelaxation2.tikz}
    \input{figures/starRelaxation3.tikz}
    \input{figures/starRelaxation4.tikz}
    \input{figures/starRelaxation5.tikz}
    \input{figures/starRelaxation6.tikz}
  \end{center}
  \caption{\label{fig:starShape} A initially star-shaped
  semi-permeable vesicle in a shear quiescent flow with $\beta=1$. Note
  that the time steps are not equispaced.}
\end{figure}

\begin{figure}[htp]
  \input{figures/starAreaDeriv.tikz}
  \qquad
  \input{figures/starTension.tikz}
  \caption{\label{fig:starArea} (a) The area (red) and its derivative
  (blue) of an initially star-shaped vesicle as a function of time. The
  dots correspond to the time steps shown in Figure~\ref{fig:starShape}.
  (b) The tension of the vesicles illustrated in
  Figure~\ref{fig:starShape}.  The tension at the time horizon $T=1$ is
  also included. At this point, the vesicle is nearly circular and the
  tension agrees with the constant value from
  equation~\eqref{eqn:finalTension}. This dashed black line corresponds
  to this constant tension value.}
\end{figure}

>>>>

We consider a single semi-permeable vesicle in a quiescent flow. For
impermeable vesicles, the vesicle relaxes to a shape where the tension
$\Lambda$ is constant and negative~\cite{kra-win-sei-lip1996}. In the
semi-permeable case, the area of the vesicle is governed by
equation~\eqref{eqn:areaROC}, where $\beta > 0$. Therefore, when the
semi-permeable vesicle reaches a steady-state shape, we have
\begin{align}
  \int_{\gamma} \left(-\frac{\kappa^3}{2} + \kappa \Lambda \right) \, ds
  = 0.
\end{align}
Based on numerical observations, the steady-state shape is a circular
vesicle with constant tension. Since the tension and curvature are
constant, we can solve for the curvature in terms of the tension $\kappa
= \sqrt{2\Lambda}$. Therefore, the steady state shape is a circle of
radius $r = 1/\sqrt{2\Lambda}$, and therefore the length is
\begin{align}
  L = \frac{\sqrt{2}\pi}{\sqrt{\Lambda}},
\end{align}
which is constant by the local inextensibility constraint. Finally, we
can compute the final tension in terms of the length using the formula
\begin{align}
  \Lambda = \frac{2\pi^2}{L^2}.
  \label{eqn:finalTension}
\end{align}
Therefore, in contrast to a impermeable vesicle, the final tension is
positive rather than negative.

We start by simulating a star-shaped vesicle in a quiescent flow with
semi-permeability rate $\beta=1$ (Figure~\ref{fig:starShape}). To
perform this simulation, we use an adaptive second-order time stepping
method~\cite{qua-bir2016}. The times and reduced areas are in the
titles, and note that the shapes are not eqiuspaced in time.
\begin{figure}[htp]
  \begin{minipage}{0.55\textwidth}
    \input{figures/starRelaxation1.tikz}
    \input{figures/starRelaxation2.tikz}
    \input{figures/starRelaxation3.tikz}
    \input{figures/starRelaxation4.tikz}
    \input{figures/starRelaxation5.tikz}
    \input{figures/starRelaxation6.tikz}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\textwidth}
  \input{figures/starAreaDeriv.tikz}
  \end{minipage}
  \caption{\label{fig:starShape} A initially star-shaped semi-permeable
  vesicle in a shear quiescent flow with $\beta=1$. Note that the time
  steps are not equispaced. The area (red) and its derivative (blue) of
  an initially star-shaped vesicle as a function of time. The dots
  correspond to the time steps shown in six time steps
  show on the left.}
\end{figure}

\begin{figure}[htp]
\begin{minipage}{0.40\textwidth}
\input{figures/starTension.tikz}
\end{minipage}
\hfill
\begin{minipage}{0.55\textwidth}
  \centering
\includegraphics[width=0.32\textwidth]{figures/StarTensionTime1.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarTensionTime2.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarTensionTime3.pdf} \\
\includegraphics[width=0.32\textwidth]{figures/StarTensionTime4.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarTensionTime5.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarTensionTime6.pdf}
\end{minipage}
  \caption{\label{fig:starTension} The tension of the time steps shown
  in Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$
  is also included. At this point, the vesicle is nearly circular and
  the tension is constant and positive. The constant is given by
  equation~\eqref{eqn:finalTension}, and this value corresponds to the
  dashed black line.}
\end{figure}

\begin{figure}[htp]
\begin{minipage}{0.40\textwidth}
\input{figures/starFlux.tikz}
\end{minipage}
\hfill
\begin{minipage}{0.55\textwidth}
\includegraphics[width=0.32\textwidth]{figures/StarFluxTime1.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarFluxTime2.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarFluxTime3.pdf} \\
\includegraphics[width=0.32\textwidth]{figures/StarFluxTime4.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarFluxTime5.pdf}
\includegraphics[width=0.32\textwidth]{figures/StarFluxTime6.pdf}
\end{minipage}
  \caption{\label{fig:starFlux} The flux of the time steps shown in
  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
  also included. At this point, the vesicle is nearly circular and there
  is no flux.}
\end{figure}

%\begin{figure}[htp]
%  \input{figures/starFlux.tikz}
%  \caption{\label{fig:starFlux} The flux of the time steps shown in
%  Figure~\ref{fig:starShape}. The tension at the time horizon $T=1$ is
%  also included. At this point, the vesicle is nearly circular and their
%  is no flux.}
%\end{figure}
